\documentclass{article}
\usepackage{times}
\usepackage{fullpage}
\usepackage{latexsym}
\usepackage{amssymb}

\newenvironment{denseenumerate}% like denseenumerate but with less separation
	{\begin{enumerate}\setlength{\itemsep}{0pt}\setlength{\parsep}{0pt}}% 
	{\end{enumerate}}


\begin{document}

\begin{center}
{\large\bf Luis von Ahn}
\end{center}

\begin{flushleft}
\begin{tabular}{p{3.75in}l}
A. Nico Habermann Associate Professor of Computer Science      & (412) 268-2813 (voice)\\
School of Computer Science & \\
Carnegie Mellon University            & {\tt biglou@cs.cmu.edu} (e-mail)\\
Pittsburgh, PA 15213     & \verb+http://www.cs.cmu.edu/~biglou/+\\
\end{tabular}
\end{flushleft}

\section*{Education}

\begin{tabular}{ll}
2000 B.S., Duke University & Mathematics\\
2003 M.S., Carnegie Mellon University & Computer Science\\
2005 Ph.D., Carnegie Mellon University & Computer Science\\
\end{tabular}

\section*{Employment Experience}

\begin{tabular}{ll}
2011-- & A. Nico Habermann Associate Professor, Computer Science Department, Carnegie Mellon University\\
2009--2011 & Staff Research Scientist, Google, Inc.\\
2008--2009 & Founder and CEO, reCAPTCHA, Inc. (acquired by Google)\\
2006--2011 & Assistant Professor, Computer Science Department, Carnegie Mellon University\\
2005--2006 & Post-Doctoral Fellow, Computer Science Department, Carnegie Mellon University\\
\end{tabular}

\section*{Related Publications}

\begin{denseenumerate}
\item Edith Law and Luis von Ahn. {\em Human Computation}. Morgan \& 
Claypool Synthesis Lectures on Artificial Intelligence and Machine 
Learning, August 2011.

\item Luis von Ahn, Ben Maurer, Colin McMillen, David Abraham and 
Manuel Blum. ``reCAPTCHA: Human-Based Character Recognition via Web 
Security Measures.'' In {\em Science}, September 12, 2008, 
pp.~1465--1468.

\item Luis von Ahn and Laura Dabbish. ``Designing Games with a 
Purpose.'' In {\em Communications of the ACM}, August 2008, 
pp.~58--67.

\item Luis von Ahn, Ruoran Liu and Manuel Blum. ``Peekaboom: A Game 
for Locating Objects in Images.'' In {\em ACM Conference on Human 
Factors in Computing Systems, CHI 2006}, pp.~55--64.

\item Luis von Ahn and Laura Dabbish. ``Labeling Images with a 
Computer Game.'' In {\em ACM Conference on Human Factors in 
Computing Systems, CHI 2004}, pp.~319--326.
\end{denseenumerate}

\section*{Other Publications}
\begin{denseenumerate}
\item Luis von Ahn, Shiry Ginosar, Mihir Kedia and Manuel Blum. 
``Improving Accessibility of the Web with a Computer Game.'' In 
{\em ACM Conference on Human Factors in Computing Systems, CHI 
Notes 2006}, pp.~79--82.

\item Luis von Ahn, Nicholas Hopper and John Langford. ``Covert 
Two-Party Computation.'' In {\em Proceedings of the Symposium on 
the Theory of Computing (STOC) 2005}, pp.~513--522.

\item Luis von Ahn, Manuel Blum and John Langford. ``How Lazy 
Cryptographers do AI.'' In {\em Communications of the ACM}, 
February 2004, pp.~56--60.

\item Luis von Ahn, Manuel Blum, Nicholas Hopper and John Langford. 
``CAPTCHA: Using Hard AI Problems for Security.'' In {\em Advances 
in Cryptology, Eurocrypt 2003}, pp.~294--311.

\item Nicholas Hopper, John Langford and Luis Von Ahn. ``Provably 
Secure Steganography.'' In {\em Advances in Cryptology, CRYPTO 
2002}, pp.~77--92.
\end{denseenumerate}

\section*{Synergistic Activities}
\begin{denseenumerate}
\item Mentored or supervised 25 undergraduates at Carnegie Mellon University. 
Among them: Yinmeng Zhang (NSF REU 2005), Mihir Kedia (NSF REU 2005), 
Ruoran Liu (NSF REU 2005), Shiry Ginosar (NSF REU 2005), Andrew Bortz 
(NSF REU 2003). Out of this work, six papers have been published at top 
conferences, and four have been presented by the students themselves. 
Some of the students have gone on to Stanford, Berkeley, CMU, MIT, and 
University of California at San Diego.

\item Co-chair and steering committee member: Human Computation Workshop 
2009, 2010, 2011, 2012.

\item Co-chair: Collective Intelligence Conference (CI 2012).

\item Founder of reCAPTCHA, Inc., in 2008. Sold to Google, Inc., in September 
2009.

\item Luis von Ahn. ``Method for Labeling Images through a Computer Game.''
United States Patent Application 20050014118. Filed June 24, 2004. 
Licensed to Google, Inc.
\end{denseenumerate}

\section*{Recent Collaborators}
\begin{denseenumerate}
\item David Abraham, Google 
\item Manuel Blum, Carnegie Mellon University 
\item Mike Crawford, Google
\item Laura Dabbish, Carnegie Mellon University
\item Roger Dannenberg, Carnegie Mellon University 
\item Severin Hacker, Carnegie Mellon University 
\item Mihir Kedia, Facebook 
\item John Langford, Microsoft
\item Edith Law, Carnegie Mellon University 
\item Ben Maurer, Facebook 
\item Colin McMillen, Google
\item Anthony Tomasic, Carnegie Mellon University
\end{denseenumerate}

\section*{Thesis Advisees}
\begin{denseenumerate}
\item Severin Hacker, Carnegie Mellon University
\item Edith Law, Carnegie Mellon University
\item Brendan Meeder, Carnegie Mellon University
\end{denseenumerate}

\section*{Graduate Advisor}
Manuel Blum, Carnegie Mellon University

%
\end{document}
